---
title: "R Notebook"
output: html_notebook
---



The Source command both executes the sourceCpp function and monitors the results of the compilation for errors. If errors do occur then the gcc error log is parsed into a navigable list:

```{r warning=FALSE}
library(Rcpp)

setwd(src)
sourceCpp("convolve.cpp")

x <- matrix(rnorm(10))
y <- matrix(rnorm(10))

convolveCpp(x, y)
```

Note that you can also check the Source on Save option to automatically source the C++ file every time it is saved. This variation will keep the keyboard focus within the editor whereas the Source command will move focus to the console.



## Inline

```{r}
library(inline)

src <- '
  Rcpp::NumericVector xa(a);
  Rcpp::NumericVector xb(b);
  int n_xa = xa.size(), n_xb = xb.size();
  Rcpp::NumericVector xab(n_xa + n_xb - 1);

 for (int i = 0; i < n_xa; i++)
  for (int j = 0; j < n_xb; j++)
    xab[i + j] += xa[i] * xb[j];
 return xab;'
```


```{r}
fun <- cxxfunction(signature(a = "numeric", b = "numeric"), src, plugin = "Rcpp")

fun(1:3, 1:4)
```



