---
title: "rcconv compile C code"
output: html_notebook
---

Load these functions first. They will compile and load.

```{r}
cLoad <- function(cFile) {
  setwd(src)
  if (.Platform$OS.type == "windows") dyn.load(paste(cFile, "dll", sep = "."))
  if (.Platform$OS.type == "unix")    dyn.load(paste(cFile, "so", sep = "."))
}

cCompile <- function(cFilec) {
  setwd(src)
  system(paste("R CMD SHLIB", cFilec))
}
```


"Observe that we convert all arguments to the approriate type (just to be sure). The .C function returns a list with all its arguments, we only need the last (fourth) argument. In this case we did not name the last argument but extracted it using a numeric index. Whether one uses named arguments (as in Section 5.1) or numeric indices is a matter of personal preference."

With a little bit more trouble we can vectorize this, 
i.e. make it accept a vector of lags and return a vector of 
convolutions of the same length. The C code now becomes:


```{r warning=FALSE}
# wrapper function to invoke cconv 

rconv <- function(lag, x) {
  cCompile("cconv.c")
  cLoad("cconv")
  
 result <- .C("cconv",
  as.integer(lag),
  as.double(x),
  as.integer(length(x)),
  as.double(0.0))[[4]]
 return(result)
}

x <- rnorm(100)
rconv(0, x)
```

```{r warning=FALSE}
rconv2 <- function(lag, x) {
  cCompile("cconv2.c")
  cLoad("cconv2")
  
  .C("cconv2",
  as.integer(lag),
  as.integer(length(lag)),
  as.double(x),
  as.integer(length(x)),
  as.double(vector("double",length(lag))))[[5]]
}

x <- rnorm(100)
rconv(1, x)
```




